---
title: "Template markdown"
author: "Kevin Greenberg"
date: "11/7/2020"
output:
  html_document: default
  pdf_document: default
---
# Challenger dataset {#anchortop}
The dataset looks at the challenger test flights, specifically the o-rings that were under stress based on the temperature and pressure. The purpose of here is to provide a basc template for presenting basic statitics and visualizations for the dataset. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(stats)
library(tidyverse)
library(sjPlot)
launch <- read.csv("challenger.csv")
```


## Summary statistics for the data 
```{r challenger, comment = '', echo=FALSE}
knitr::kable(summary(launch))
```


```{r lm, echo=TRUE, tidy=TRUE}
lm1 <- lm(distress_ct ~ temperature, data = launch)
lm2 <- lm(distress_ct ~ temperature + pressure, data = launch)
lm3 <- lm(distress_ct ~ temperature * pressure, data = launch) 
tab_model(lm1,lm2,lm3, file="output.html")
```
Jump to [top](#anchortop)

The different linear regression models do not significantly vary, indicating the simplest model is the most effective in terms accounting for variance and efficiency.
```{r lm compaison, echo=FALSE}
knitr::kable(anova(lm1, lm2, lm3))
```

```{r plots, echo=FALSE}
launch$distress_ct <- as.factor(launch$distress_ct)
launch$pressure <- as.factor(launch$pressure)

ggplot(launch, aes(x=distress_ct, y=temperature)) + 
  geom_point(aes(shape=pressure, col=pressure)) +
  labs(y="Temperature (F)", 
       x="Number of distressed o-rings", 
       title="Number of distressed o-rings by temperature", 
       caption = "Source: challenger.csv")

```


Return to [Kevin Greenberg's Portfolio](https://www.espn.com/) 